\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%-- RESUME Starts Here -------
\begin{document}
	\fontfamily{lmss}\selectfont
	\begin{center}
    	{\Huge \scshape Piyush Jaipuriyar} \\ \vspace{1pt}
    	\small \raisebox{-0.1\height}\faPhone\ +91 8447501223 ~ \href{mailto:piyushjaipuriyar@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{piyushjaipuriyar@gmail.com}} ~ 
    	\href{https://www.linkedin.com/in/piyush-jaipuriyar/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/piyush-jaipuriyar}}  ~
    	\href{https://github.com/TheAlakazam/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/TheAlakazam}}
    	\vspace{-8pt}
	\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Languages}{: Javascript, Typescript, Java, Python, C/C++, SQL, Rust} \\
   \textbf{Technologies}{: React.js, Redux, Express.js, Jest, Enzyme, Cypress, Docker, Spring Boot, Spring, JUnit, MonogDB, Oracle SQL} \\
   \textbf{Tools}{: Git, Bash, Jira} \\
  }}
\end{itemize}
\vspace{-16pt}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
	{PayPal India Pvt. Ltd.}{August 2020 -- Present}
	{Software Development Engineer 1}{Chennai, Tamil Nadu}
	\resumeItemListStart
	  \resumeItem{Developed an extensible multi-tenant UI for Case Management software used for Due Diligence investigations. 
	  Onboarded 3 subsidaries as tenants, along with the existing Paypal customers, migrating from spreadsheet and document based investigations.
	  Providing a unified User Experience across tenants, increasing investigator productivity.}
	  \resumeItem{Developed UI for multiple types of Cases used by investigators for Due Diligence on Paypal's and subsidary's customers and merchants.}
	  \resumeItem{Improved Unit Test coverage of React application from 52\% to 92\%, covering 24,000 lines of code, using Enzyme and Jest.}
	  \resumeItem{Implemented automated End-to-End testing for web application, using Cypress. Decreasing regression testing times by 60\%.}
	  \resumeItem{Developed multiple UI widgets, which are being used across teams to view and interact with user and merchant data.}
	  \resumeItem{Responsible for developing and maintaining the frontend for Due Diligence tool used by investigators.}
	  \resumeItemListEnd

  \resumeSubheading
	{PayPal India Pvt. Ltd.}{June 2019 -- July 2019}
	{Software Development Intern}{Chennai, Tamil Nadu}
	\resumeItemListStart
		\resumeItem{Developed a React.js application to manage configuration files used for internal periodic batch jobs.
		 Improved from the existing manual system being used in the organisation.}
		\resumeItem{Worked on REST API written using Spring Boot to interface with the configuration files.}
  	\resumeItemListEnd

  \resumeSubheading
  	{JMoon Technologies Pvt. Ltd.}{June 2018 -- June 2018}
	{Software Development Intern}{New Delhi}
	\resumeItemListStart
		\resumeItem{Developed a library to communicate and run Dynamixel actuators. 
		Migrating from the current library using Python, to using official C++ SDK by the manufacturers and wrapping in Python for ease of use.} %-- Improvement percentage needed (STAR)
		\resumeItem{Researched on various offline Speech-to-Text engines, to deploy on development boards like Raspberry Pi.}
	\resumeItemListEnd
  
\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
	\resumeSubheading
		{SRM Institute of Science and Technology}{2016 -- 2020}
		{Bachelor of Technology in Computer Science and Engineering}{Chennai}
	\resumeSubSubheading{CGPA: 9.0}{}
	
	\resumeSubheading
		{Class 12th}{2014 -- 2016}
		{Delhi Public School, Noida}{Noida, Uttar Pradesh}
	\resumeSubSubheading{CBSE Board: 90\%}{}
\resumeSubHeadingListEnd

% %-----------PROJECTS-----------
\section{Projects}
  \vspace{-5pt}
  \resumeSubHeadingListStart
	\resumeProjectHeading
		{\textbf{coreutils} $|$ \emph{Rust, CLI Tools, Open Source}}{}
		\resumeItemListStart
		  \resumeItem{Added option to use blake2 as a hashing algorithm for the hashsum tool}
		\resumeItemListEnd
		\vspace{-13pt}
	\resumeProjectHeading
		{\textbf{Dyamixel Motor Library} $|$ \emph{Python}}{}
		\resumeItemListStart
		  \resumeItem{Developed interface to use the DynamixelSDK to control and communicate with the Dynamixel motors}
		  \resumeItem{Packaged as a python package for easy installation}
		\resumeItemListEnd 
  \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------INVOLVEMENT---------------
\section{Achievements / Awards}
	\resumeItemListStart
		\resumeItem{Placed 3rd at inhouse Hackathon, developed VS Code extension to provide autocompletion suggestions for in-house Document-as-Code JSON files used for rendering UI components, using Language Server Protocol.}
		\resumeItem{Placed in Top 10 in company wide Capture the Flag event.}
		\resumeItem{Participated in RoboGames 2018 (International Robotics Competition), winning 2 Gold and 1 Bronze medals.}
	\resumeItemListEnd

\end{document}